\documentclass[a4paper]{article}
\usepackage[a4paper, total={17cm, 24cm}]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{tikz}
\usepackage{blindtext}
\usepackage{braket}
\usepackage{physics}

\setlength\parindent{0pt}
\setlength\parskip{1em}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\I}{\mathbb{I}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\C}{\mathbb{C}}

\newcommand{\bb}[1]{\textbf{#1}}
\newcommand{\ov}[1]{\overline{#1}}
\newcommand{\ova}[1]{\overrightarrow{#1}}

	\title{Related Work on Reddit}	
	\author{Carel Kuusk}
	\date{\vspace{-5ex}}
\begin{document}
\maketitle

\section*{Related work}

The aim of this project is to get a better sense of how Reddit evolved in its first years. For this we will be analyzing 
the network structure of comments from 2005 to 2008. Possible analysis methods are provided in Cordeiro et al. (2018): snapshot analysis 
to identify more static features of the network structure and aggregate analysis (either via landmark windows or sliding windows) for 
analysing statistical properties of the graphs within a certain timeframe.

Troy Steinbauer has analyzed the overall properties of the Reddit network in 2011. He identified that for example related subreddit distribution was 
following the expected power-law distribution.

The behaviour of individual users was analyzed by Thukral et al in 2018. The analysis was partly done on the 2008 and partly on the 2014-2015 period. 
They discovered, that based on the commenting and posting patterns, the users can be clustered into three types based on when most of their contributions are made 
(either within a short period from sign-up, stably, or more actively after a long hibernation). Also they discovered a clear separation between commenters and posters.


\section*{References}

Mário Cordeiro, Rui P. Sarmento, Pavel Brazdil and João Gama (October 31st 2018). Evolving Networks and Social Network Analysis Methods and Techniques, Social Media and Journalism - Trends, Connections, Implications, Ján Višňovský and Jana Radošinská, IntechOpen, DOI: 10.5772/intechopen.79041. Available from: https://www.intechopen.com/books/social-media-and-journalism-trends-connections-implications/evolving-networks-and-social-network-analysis-methods-and-techniques

Troy Steinbauer (2011) Information and Social Analysis of Reddit. Available at: http://snap.stanford.edu/class/cs224w-2011/proj/tbower\_Finalwriteup\_v1.pdf 

Sachin Thukral, Hardik Meisheri, Tushar Kataria, Aman Agarwal, Ishan Verma, Arnab Chatterjee, Lipika Dey (2018) Analyzing behavioral trends in community driven discussion platforms like Reddit. arXiv:1809.07087
\end{document}
